---
title: "flat_main.Rmd empty"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
```

<!--
You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.
-->

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```


#### Install `nimble`

If you never used the package `nimble`, you first need to install it following recommendations [here](https://r-nimble.org/download)



# Run a single model

The function `Gro_run()` allows to run one growth model. This function takes as arguments:

* `x` the index of the formula to use 
* `dat` including at least the numeric columns *Age*, *MeasurementValue* and *AnimalAnonID* 
* `all_mods` a vector of model names. The following models are supported : logistic, gompertz, tpgm, power, richards, vonbertalanffy.
* `random` list of the model names giving the parameters that should be included an individual random effect
* `run`: a list of Bayesian parameters including `nch` number of chains, `nthin` interval between iterations to keep, `nburnin` number of iterations to discard and `niter` total number of iterations. The default number of iterations is too small and need to be increased to reach convergence.

Only the model of index `x` will be used to run the model. 

The function returns:

* `model` a list including estimates of coefficients and model characteristics
* `tab` a data frame with information on model wAIC




```{r function-gro_run}
#' Run growth model
#' 
#' Build and run the bayesian growth model `x` of `all_mods`.
#' 
#' @param x \code{numeric} index of the formula used to build the model
#' @param all_mods \code{vector of characters} of model names. The following models are supported: logistic, gompertz, tpgm, power, richards, vonbertalanffy.
#' @param dat \code{data.frame}including at least the numeric columns *age*, *z* and *IND*
#' @param random {vector of character} of the same length as \code{all_mods} giving the parameters that should be included an individual random effect
#' @param run \code{list} Bayesian parameters. They should be increased to reach convergence \itemize{
#' \item \code{nch} number of chains.
#' \item \code{nthin} interval between iterations to keep.
#' \item \code{nburnin} number of iterations to discard.
#' \item \code{nit} total number of iterations.
#' }
#'
#' @return This function returns a \code{list}:
#'         \itemize{
#'           \item \code{model} a list including estimates of coefficients and model characteristics
#'           \item \code{tab} a data frame with information on models & WAIC
#'           }
#' 
#' @import dplyr assertthat nimble
#' 
#' @export
Gro_run<-function(x, 
                  dat,
                  all_mods,
                  random = "",
                  run = list(nit = 100, nburnin = 10, nthin = 1, nch = 1)){
  
  assert_that(is.numeric(x))
  assert_that(x>0)
  assert_that(is.vector(all_mods))
  assert_that(is.character(all_mods))
  assert_that(x<= length(all_mods))
  assert_that(is.data.frame(dat))
  assert_that(dat %has_name% c('age', 'z', 'IND'))
  assert_that(is.numeric(dat$age))
  assert_that(is.numeric(dat$z))
  assert_that(run %has_name% c("nit", "nburnin", "nthin", "nch"))
  assert_that(is.character(random))
  model_type=all_mods[x]
  random_mod = strsplit(random[x], 
                        paste(c(","," ", ";"), collapse = "|"))%>%
    unlist%>%
    stringi::stri_remove_empty()
  
  model_gro<-Gro_ModSettings(dat, random = random_mod, mod =  model_type)
  
  param = stringr::str_subset(model_gro$parameters, '_', negate = T)
  if(length(random_mod)>1){
    for(r in random_mod){
      assert_that(r %in% param, msg = glue::glue("{r} is not a parameter of the model}"))
    }
  }
  model_nimble = Gro_writenimblecode(params = param, 
                                     model = model_gro$model_nim,
                                     random = random_mod,
                                     maxval = model_gro$maxval, 
                                     minval= model_gro$minval
  )
  outnim <- runnimble(model = model_nimble,
                      const = model_gro$const_nim,
                      data_nim =  model_gro$data_nim,
                      inits_nim = model_gro$inits_nim,
                      param = model_gro$parameters,
                      run = run,
                      model_type = model_type,
                      x = x)
  
  out=list()
  out$model=list(model_type = model_type,
                 random = random_mod,
                 coef = as.data.frame(outnim$coef),
                 run = run,
                 params = param,
                 model_fun = model_gro$model_fun
  )
  
  out$tab <- data.frame(
    model_type = model_type,
    random = stringr::str_c(random_mod, collapse = ", "),
    index = x,
    Nparam =  (length(model_gro$param)-1),
    WAIC = outnim$WAIC$WAIC,
    lppd = outnim$WAIC$lppd
    
  )
  return(out)
}
```


```{r example-gro_run}
age <- rnorm(10000, 0, 1)
id1 =  rnorm(21,0, 0.5)
id2 =  rnorm(21,0, 0.4)
id3 =  rnorm(21,0, 0.3)
IND =sample(c(1:20), 100, replace = TRUE)
z <- 0.2+ id1[IND]+ (15 + id2[IND])* (1 - exp(-(1+ id3[IND]) * age)) +
  rnorm(100, 0, 0.01)
dat = data.frame(age = age, z = z, 
                 IND = as.numeric(factor(IND ,labels = c(1:length(unique(IND)))))
)

#Run a vonbertalanffy model including an individual effect on z0
out = Gro_run(1, 
              dat,
              all_mods  = c("vonbertalanffy"),
              random = c("z0"),
              run = list(nit = 5000, nburnin = 1000, nthin = 10, nch = 3))
out$tab

```


```{r tests-Gro_run}
age <- rnorm(10000, 0, 1)
id1 =  rnorm(21,0, 0.5)
IND =sample(c(1:20), 100, replace = TRUE)
z <- 0.2+ id1[IND]+ (15 )* (1 - exp(-(1) * age)) +rnorm(100, 0, 0.01)
dat = data.frame(age = age, z = z, IND = as.numeric(factor(IND , labels = c(1:length(unique(IND)))))
)

test_that("Gro_run work", {
  a = Gro_run(1, 
              all_mods  = c("vonbertalanffy", "gompertz"),
              dat,random = c("z0"),
              run = list(nit = 1000, nburnin = 100, nthin = 1, nch = 1))
  expect_named(a,c("model","tab"))
  expect_equal(a$model$coef%>%
                 nrow, 900 )
  expect_named(a$tab, c("model_type", "random", "index","Nparam", "WAIC", "lppd"))
})

```




# Growth analysis: run multiple models
This function fits a series of growth models to a dataset, and select the best one by wAIC. It takes as arguments:

* data_weight including at least the numeric columns *Age*, *MeasurementValue* and *AnimalAnonID* 
* all_mods indicating the growth models that need to be fit.The following models are supported : logistic, gompertz, tpgm, power, richards, vonbertalanffy. default = "vonBertalanffy"
* `random` list of the model names giving the parameters that should include an individual random effect. See the example


```{r function-Gro_analysis}

#' Growth model selection
#' 
#' This function fit a series of growth models to a dataset and select the best one by wAIC.
#' 
#' @param data_weight \code{data.frame} including at least the numeric columns *Age*, *MeasurementValue* and *AnimalAnonID* 
#' @param all_mods \code{vector of character} indicating the growth models that need to be fit.The following models are supported :logistic, gompertz, tpgm, power, richards, vonbertalanffy. default = "vonBertalanffy"
#' @param random {list} of the model names giving the parameters that should include an individual random effect. See the example
#' @param logtransform {logical} whether age and measurement values should be log transform (+1 is added to avoid having log(0))
#' @param run \code{list} Bayesian parameters. They should be increased to reach convergence \itemize{
#' \item \code{nch} number of chains.
#' \item \code{nthin} interval between iterations to keep.
#' \item \code{nburnin} number of iterations to discard.
#' \item \code{nit} total number of iterations.}
#' @param parallel \code{logical} Whether the model should be run in parallel
#' 
#' @import dplyr assertthat
#' @importFrom parallel detectCores parLapply makeCluster stopCluster
#' 
#' @return a list including:
#' * model: the fit of the best model
#' * the wAIC table of the model
#' 
#' @export
Gro_analysis <- function(data_weight, 
                         all_mods =c("vonbertalanffy"),
                         random = list(),logtransform = FALSE,
                         run = list(nit = 100, nburnin = 10, nthin = 1, nch = 1),
                         parallel= FALSE
) {
  assert_that(is.logical(parallel))
  assert_that(all(all_mods %in% c("logistic", "gompertz", "richards", "vonbertalanffy", "tpgm", "power", "richard")), msg = "The growth models supported are: logistic, gompertz, tpgm, power, richards, vonbertalanffy")
  assert_that(is.data.frame(data_weight))
  assert_that(data_weight %has_name% c("MeasurementValue","Age", 'AnimalAnonID'))
  assert_that(all(data_weight$Age >= 0 ))
  assert_that(all(data_weight$MeasurementValue > 0 ))
  if(length(random)>1){
    assert_that(is.list(random))
    assert_that(all(names(random) %in% all_mods))
  }
  
  if (logtransform){
  data_weight<-data_weight%>%
    mutate(age = log(Age + 1),
           z = log(MeasurementValue + 1),
           IND = as.numeric(factor(AnimalAnonID, labels = c(1:length(unique(AnimalAnonID))))))
  }else{
      data_weight<-data_weight%>%
    mutate(age = Age ,
           z = MeasurementValue ,
           IND = as.numeric(factor(AnimalAnonID, labels = c(1:length(unique(AnimalAnonID))))))

  }
  
  #Fitting the different growth models
  all_fits_tab=c()
  all_fits <- list()
  
  models = rep(names(random),as.vector(sapply(random, length)))
  miss = setdiff(all_mods,names(random))
  models = c(models, miss)
  randoms = c(unlist(random), rep('',length(miss)))
  #Fit models
    ### parallelize?
  if (parallel){
    n_cores <- detectCores()
    clust <- makeCluster(n_cores)
  }
  if(parallel) {
    all_fits <- parLapply(clust, 1:length(models),
                          Gro_run,
                          all_mods = models,
                          random = randoms,
                          dat = data_weight,
                          run = run
    )
    
  }  else {
    writeLines("\t* parallel has been set to FALSE, please wait more !")
    all_fits <- pbapply::pblapply(1:length(models),
                                  Gro_run,
                                  all_mods = models,
                                  random = randoms,
                                  dat = data_weight,
                                  run = run
    )
  }
  
  all_fits_tab=c()
  for (i in 1:length(all_fits)){
    all_fits_tab <- rbind(all_fits_tab,all_fits[[i]]$tab)
  }
  all_fits_tab <- all_fits_tab%>% arrange(WAIC)
  best_std <- all_fits[[as.numeric(all_fits_tab[1, "index"]) ]]$model
  if(parallel) {
    stopCluster(clust)
  }
  best_std$logtransform= logtransform
  
  all_fits_tab <- all_fits_tab%>% 
    dplyr::select(-index)
  
  return(list(model = best_std,
              wAIC_tab =all_fits_tab)
  )
}
```

```{r example-Gro_analysis}
Age <- sample(c(0:10), 1000, replace = TRUE)
MeasurementValue <- exp(0.2+15 * (1 - exp(-(0.1) * log(Age+1)))+ rnorm(1000,0,0.01))-1 
AnimalAnonID <- sample(c(0:20), 100, replace = TRUE)
dat = data.frame(Age = Age, MeasurementValue = MeasurementValue, 
                 AnimalAnonID = AnimalAnonID, MeasurementType = "Live Weight")

#Test 4 models: vonbertalanffy including an individual random effect on z0
#               vonbertalanffy including individual random effects on z0 and zinf
#               gompertz including an individual random effect on gamma 
#               gompertz including no individual random effect
a = Gro_analysis(dat, all_mods  = c("vonbertalanffy", "gompertz"),
                 random = list(vonbertalanffy = c("z0", "z0, zinf"), gompertz = c("gamma", "")),
                 run = list(nit = 1000, nburnin = 100, nthin = 1, nch = 1))
```

```{r tests-Gro_analysis}
Age <- sample(c(0:10), 1000, replace = TRUE)
MeasurementValue <- exp(0.2+15 * (1 - exp(-(0.1) * log(Age+1)))+ rnorm(1000,0,0.01))-1 
AnimalAnonID <- sample(c(0:20), 100, replace = TRUE)
dat = data.frame(Age = Age, MeasurementValue = MeasurementValue, 
                 AnimalAnonID = AnimalAnonID, MeasurementType = "Live Weight")

test_that(
  "Gro_analysis works",
  { 
    out = Gro_analysis(dat, all_mods  = c("vonbertalanffy"),
                       random = list(vonbertalanffy = c("z0", "z0, zinf")),
                       run = list(nit = 100, nburnin = 10, nthin = 1, nch = 1))
    
    expect_named(out,c( "model", "wAIC_tab"))
    expect_named(out$wAIC_tab,c("model_type", "random","Nparam","WAIC","lppd" ))
  })
```


# Growth Model Setting

This function gets the parameter and equations for the growth model and takes as arguments:

* `data`, a data frame including at least the numeric columns *age*, *z* and *IND*
* `random`  name of the parameters that must include an individual random effect
* `mod` Name of the model to fit. The following models are supported : logistic, gompertz, tpgm, power, richards, vonbertalanffy.


```{r function-Gro_ModSettings}

#' Growth model settings
#' 
#' This function gets the parameter and equations for the growth model
#' 
#' @param data \code{data.frame} including at least the numeric columns *age* and *z* 
#' @param random \code{vector of character} name of the parameters that must include an individual random effect
#' @param mod \code{character} Name of the model to fit. The following models are supported : logistic, gompertz, tpgm, power, richards, vonbertalanffy
#' 
#' 
#' @import dplyr assertthat
#' @importFrom nimble nimbleFunction 
#'
#' @return a list including the function of the growth model,  the number of parameter, their names, their initial values and their lowest possible values
#' 
#' @export
# Set growth model parameters:
Gro_ModSettings <- function(data, random =NULL, mod = "vonbertalanffy") {
  
  assert_that(mod %in% c("logistic", "gompertz", "richards", "vonbertalanffy", "tpgm", "power", "richard"), msg = "The growth models supported are: logistic, gompertz, tpgm, power, richards, vonbertalanffy")
  assert_that(is.data.frame(data))
  assert_that(data %has_name% c('age', 'z', 'IND'))
  assert_that(is.numeric(data$age))
  assert_that(is.numeric(data$z))
  if(length(random)>0) {
    assert_that(is.character(random))
  }
  if(mod == "vonbertalanffy"){
    
    model_nim <- "
   for (j in 1:N){{
       z[j] ~dnorm(z0[IND[j]] + (zinf[IND[j]] - z0[IND[j]]) *
    (1 - exp(- gamma[IND[j]] * age[j])), sigma_res)}}"
    model <- function(age,coef){
      coef$mu_z0 + (coef$mu_zinf-coef$mu_z0) * (1 - exp(- coef$mu_gamma * age))
    }
    
    inits <-  list(mu_z0= min(exp(data$z)),
                 mu_zinf = max(data$z),
                 mu_gamma = 0.1, sigma_res  = 1
                 
                 
                 
  )
  maxval = list(z0 =  25, zinf = max(data$z)*50, gamma = 2)
  minval = list(z0 = 0, zinf = 0, gamma = 0)
  param = c("mu_z0","mu_zinf", "mu_gamma",
            "sigma_res",
            "z0", "zinf", "gamma")
  }
  
if(mod == "gompertz"){
    model_nim <- "
   for (j in 1:N){{
       z[j] ~dnorm( zinf[IND[j]] * exp(-alpha[IND[j]]*exp(- gamma[IND[j]] * age[j])), sigma_res)}}"
    model <- function(age,coef){
         coef$mu_zinf * exp(-coef$mu_alpha*exp(-mu_gamma * age))
    }
    inits <-  list(mu_alpha= 0,
                 mu_zinf = max(data$z),
                 mu_gamma = 0.1, sigma_res  = 1
                 
                 
                 
  )
  maxval = list(alpha =  40, zinf = max(data$z)*50, gamma = 2)
  minval = list(alpha = -40, zinf = 0, gamma = 0)
  param = c("mu_alpha","mu_zinf", "mu_gamma",
            "sigma_res",
            "alpha", "zinf", "gamma")
}
  
  
   if(mod == "logistic"){
    model_nim <- "
   for (j in 1:N){{
       z[j] ~dnorm(zinf[IND[j]] / (1 + exp(- gamma[IND[j]] * (age[j] - xinfl[IND[j]]))), sigma_res)}}"
    model <- function(age,coef){
           coef$mu_zinf / (1 + exp(- coef$mu_gamma * (age - coef$mu_xinfl)))
    }
     inits <-  list(mu_xinfl= mean(data$age),
                 mu_zinf = max(data$z),
                 mu_gamma = 0.1, sigma_res  = 1
                 
                 
                 
  )
  maxval = list(xinfl =  max(data$age), zinf = max(data$z)*50, gamma = 2)
  minval = list(xinfl = min(data$age), zinf = 0, gamma = 0)
  param = c("mu_xinfl","mu_zinf", "mu_gamma",
            "sigma_res",
            "xinfl", "zinf", "gamma")
 }
     if(mod == "tpgm"){
      
    model_nim <- "
   for (j in 1:N){{
       z[j] ~dnorm(zinf[IND[j]] *    (1 - exp(- gamma[IND[j]] *(1- h[IND[j]]/((age[j] -th[IND[j]])^2+1) *(age[j] - age0[IND[j]])), sigma_res)}}"
    model <- function(age,coef){
      coef$mu_zinf * (1 - exp(- coef$mu_gamma (1-coef$mu_h/((age -coef$mu_th)^2+1)) * (age - coef$mu_age0)))
    }
         inits <-  list(mu_age0= 0,
                 mu_zinf = max(data$z), mu_h = 0, mu_th = 1,
                 mu_gamma = 0.1, sigma_res  = 1
                 
                 
                 
  )
  maxval = list(age0 =  0, zinf = max(data$z)*50, gamma = 2, h= 5, th = max(data$age))
  minval = list(age0 = -20, zinf = 0, gamma = 0, h= -5, th = 0)
  param = c("mu_age0","mu_zinf", "mu_gamma","mu_h", "mu_th",
            "sigma_res",
            "age0", "zinf", "gamma", "h", "th")
}
  
     if(mod == "power"){
    model_nim <- "
   for (j in 1:N){{
       z[j] ~dnorm(alpha0[IND[j]] + alpha1[IND[j]] * (age[j]^(beta[IND[j]])), sigma_res)}}"
    model <- function(age,coef){
   
      coef$mu_alpha0 + coef$mu_alpha1 * (age)^(coef$mu_beta)
    }
      inits <-  list(mu_alpha0= 0,
                 mu_alpha1 = 1,
                 mu_beta = 1, sigma_res  = 1
                 
                 
                 
  )
  maxval = list(alpha0 =  -10, alpha1 = -10, beta = 0)
  minval = list(alpha0 = 10, alpha1 = 10, beta = 5)
  param = c("mu_alpha0","mu_alpha1", "mu_gamma",
            "sigma_res",
            "alpha0", "alpha1", "gamma")
   }
     if(mod == "richards"){
    model_nim <- "
   for (j in 1:N){{
       z[j] ~dnorm(zinf[IND[j]] * (1 - z0[IND[j]] *exp(- gamma[IND[j]] * age[j]))^(P[IND[j]]), sigma_res)}}"
    model <- function(age,coef){
  
       coef$mu_zinf * (1 - coef$mu_z0* exp(- coef$mu_gamma * age))^(P)
    }
     inits <-  list(mu_z0= 1,mu_P = 1,
                 mu_zinf = max(data$z),
                 mu_gamma = 0.1, sigma_res  = 1
                 
                 
                 
  )
  maxval = list(z0 =  25, zinf = max(data$z)*50, gamma = 2, P = 5)
  minval = list(z0 = 0, zinf = 0, gamma = 0, P = 0)
  param = c("mu_z0","mu_zinf", "mu_gamma","mu_P",
            "sigma_res",
            "z0", "zinf", "gamma", "P")
 }

  if(length(random)>0){
    for( p in random){
      param = c(param, glue("sigma_{p}")) 
      a =list(1)
      names(a) = glue("sigma_{p}")
      inits = append(inits, a)
    }
  }
  
  const <- list(N = nrow(data),
                Nind = length(unique(data$IND)),
                IND = data$IND
  )
  
  
  
  dat_nim <- list(z = data$z,
                  age = data$age
  )
  
  ARG = list(model_nim  =model_nim,
             model_fun  =model,
             const_nim = const,
             data_nim = dat_nim,
             inits_nim = inits,
             parameters = param,
             maxval = maxval,
             minval = minval
  )
  return(ARG)
  
}
```

```{r example-Gro_ModSettings}
age <- rnorm(100, 0, 1)
z <- 0.2+ 15 * (1 - exp(-(1) * age)) +rnorm(100, 0, 0.01)
dat = data.frame(age = age, z = z,IND =sample(c(0:20), 100, replace = TRUE)
)
model <- Gro_ModSettings(data = dat, mod = "vonbertalanffy")
```


```{r tests-Gro_ModSettings}
age <- rnorm(100, 0, 1)
z <- 0.2+ 15 * (1 - exp(-(1) * age)) +rnorm(100, 0, 0.01)
dat = data.frame(age = age, z = z,IND =sample(c(0:20), 100, replace = TRUE)
)

test_that(
  "Gro_ModSettings error",
  {
    expect_error(
      dat %>% Gro_ModSettings(mod = "vonBert"),
      regexp = "The growth models supported are: logistic, gompertz, tpgm, power, richards, vonbertalanffy")
    expect_error(
      dat$z %>% Gro_ModSettings(),
      regexp = "data is not a data frame")
  })



test_that(
  "Gro_ModSettings works",
  {     
    a=dat %>% Gro_ModSettings(mod = "vonbertalanffy")
  expect_named(a,
               c("model_nim","model_fun",  "const_nim",  "data_nim",   "inits_nim",  "parameters", "maxval", 'minval'))
  expect_named(a$inits_nim, c('mu_z0', 'mu_zinf', 'mu_gamma', 'sigma_res'))
  expect_named(a$data_nim, c("z", "age"))
  expect_named(a$const_nim, c("N", "Nind", "IND"))
  }
)
```


# Plot model prediction

This function gives the predicted values of the model and plots to check the convergence of the model. It takes as arguments:

* `data` including at least the numeric columns *Age*, *MeasurementValue* and *AnimalAnonID* 
* `out` result output named `model` from Gro_run() or from Gro$analysis()

It returns the following object:

*`summary`shomwing mean, standard deviation, credible interval at 95% and the Gelman-Rubin statistics Rhat of each parameter.
* `predictions` giving the mean estimates and credible interval at 95% of each age
 `GOF`: 4 tests of goodness of fit: "normal": test if residuals are normally distributes ; "X"; test if there is a trend between residual and Age, "var": Test if there is the trend in the variance of the residuals over Age ,"conv": check if all Rhat < 1.1
* `plot_pred` Plot of the predicted values, credible interval at 95% in grey and data points.
* `convergence`: Plots of the Bayesian chains 
* `posterior`: Plots of the posterior distribution for each parameter

```{r function-Gro_pred}

#' Predictions and plots
#' 
#' Give predicted values of the model and plots to check the convergence of the model
#' 
#' @param data \code{data.frame} including at least the numeric columns *Age*, *MeasurementValue* and *AnimalAnonID* 
#' @param out result output from Gro_run()
#' @param Cred_int \code{numeric} lower and upper bound of the credible interval to plot and to predict
#' @param title \code{character} Title of the plot
#' 
#' @import dplyr assertthat 
#' @importFrom ggplot2 ggplot  geom_line ggtitle geom_ribbon aes geom_point
#' @importFrom stringr str_which
#' @importFrom stats lm shapiro.test
#'
#' @return a list including \itemize{
#' \item `summary`shomwing mean, standard deviation, credible interval at 95% and the Gelman-Rubin statistics Rhat of each parameter.
#' \item `predictions` giving the mean estimates and credible interval at 95% of each age
#' \item `GOF`: 4 tests of googness of fit: "normal": test if residuals are normally distributes ; "X"; test if there is a trend between residual and Age, "var": Test if there is the trend in the variance of the residuals over Age ,"conv": check if all Rhat < 1.1
#' \item `plot_pred` Plot of the predicted values, credible interval at 95% in grey and data points.
#' \item `convergence`: Plots of the Bayesian chains 
#' \item `posterior`: Plots of the posterior distribution for each parameter
#' }
#' 
#' @export
Gro_pred <- function(data, out, Cred_int = c(0.025,0.975),title = "") {
  assert_that(is.data.frame(data))
  assert_that(data %has_name% c("MeasurementValue","Age", 'AnimalAnonID'))
  assert_that(is.numeric(data$MeasurementValue))
  assert_that(is.numeric(data$Age))
  assert_that(is.numeric(Cred_int))
  assert_that(length(Cred_int) == 2)
  assert_that(all(Cred_int<=1))
  assert_that(all(Cred_int>=0))
  assert_that("coef" %in% names(out), msg = "out must be created using function Gro_run or Gro_analysis")
  assert_that("model_fun" %in% names(out), msg = "out must be created using function Gro_run or Gro_analysis")
  
  
  toplot = c(str_which(names(out$coef), "mu"),
             str_which(names(out$coef), "sigma"))
  beta_tt <- out$coef[,toplot]
  
  
  resrb <- sum_nim(as.matrix( beta_tt), out$run$nch)
  
  
  #Plot histograms of beta
  mpl=mconv=list()
  
  for (i in 1:ncol(beta_tt)){
    mpl[[i]] <- hist_post( beta_tt[, i] )
    mconv[[i]] <- conv_plot( beta_tt[, i],  (out$run$nit-out$run$nburnin)/out$run$nthin)
    
  }
  post_pl<- cowplot::plot_grid(plotlist = mpl, 
                               align = "hv", 
                               nrow = ceiling(sqrt(ncol(beta_tt))),
                               ncol = round(sqrt(ncol(beta_tt))),
                               labels = colnames(beta_tt),
                               label_x = 0, label_y = 0, label_size = 12,
                               hjust = -0.5, vjust = -0.5
  )
  conv_pl<- cowplot::plot_grid(plotlist = mconv, 
                               align = "v", 
                               nrow = ncol(beta_tt),
                               labels = colnames(beta_tt),
                               label_x = 0, label_y = 0, label_size = 12,
                               hjust = -0.5, vjust = -0.5
  )
  
  

  
  # Predictions
  #Vector for predictions
  zQuant <- tibble(Age = seq(min(data$Age), max(data$Age)+0.1, 0.1),
                   mean = numeric(1),
                   Conf_Int_low = numeric(1),
                   Conf_Int_up = numeric(1)
  )
  
  #Fitted values and residuals
  for (j in 1:nrow(zQuant)){
      if(out$logtransform){

    pred = out$model_fun(log(zQuant$Age[j]+1),out$coef)
    zQuant$mean[j] = mean(exp(pred)-1)
    zQuant$Conf_Int_low[j] = quantile(exp(pred)-1, Cred_int[1])
    zQuant$Conf_Int_up[j] =  quantile(exp(pred)-1, Cred_int[2])
      }else{
           pred = out$model_fun(zQuant$Age[j],out$coef)
    zQuant$mean[j] = mean(pred)
    zQuant$Conf_Int_low[j] = quantile(pred, Cred_int[1])
    zQuant$Conf_Int_up[j] =  quantile(pred, Cred_int[2])

      }
  }
  
  data_pred = data%>%
    mutate(Age= round(Age,0.1))%>%
    group_by(Age)%>%
    summarize(MeasurementValue = mean(MeasurementValue))%>%
    left_join(zQuant%>%select(Age, mean), by = "Age")
  
   if(out$logtransform){
      data = data%>%
        mutate(Age = log(Age+1),
               mean = log(mean +1),
                MeasurementValue = log(MeasurementValue+1))
  }
  #GOF
  GOF = list(normal = T, X = T, var = T, conv = all(resrb$Rhat<1.1))
  ez <- data_pred$MeasurementValue - data_pred$mean
  ez2 <- ez^2
  test  = shapiro.test(ez)
  if(test$p.value<0.01){GOF$normal = FALSE}
  a = summary(lm(ez2 ~ data_pred$Age)) #test variance?
  if(a$coefficients[2,4]<0.01){GOF$X = FALSE}
  b = summary(lm(ez ~ data_pred$Age)) #test pour senescence??
  if(b$coefficients[2,4]<0.01){GOF$var = FALSE}
  
  
  
  p <- ggplot(data, aes(x = Age))+
    ggtitle(title)+
    geom_point(aes(y = MeasurementValue))+
    geom_ribbon(data = zQuant,aes ( ymin = Conf_Int_low, ymax = Conf_Int_up),
                fill = "grey80", alpha = 0.25)+
    geom_line(data = zQuant,aes ( y = mean ))
  
  
  
  return(list(summary =  resrb, 
              predictions=zQuant,
              plot_pred = p, 
              posterior =post_pl, 
              convergence = conv_pl, 
              GOF = GOF ))
}
```

```{r example-Gro_pred}
Age <- sample(c(0:10), 100, replace = TRUE)
AnimalAnonID <- sample(c(0:20), 100, replace = TRUE)
MeasurementValue <- exp(0.2+15 * (1 - exp(-(0.1) * log(Age+1)))+ 
                          rnorm(100,0,0.01) + AnimalAnonID*0.1)-1 
dat = data.frame(Age = Age, MeasurementValue = MeasurementValue, 
                 AnimalAnonID = AnimalAnonID, MeasurementType = "Live Weight")

out = Gro_analysis(dat, 
                   all_mods = c("vonbertalanffy"),
                   run = list(nit = 1000, nburnin = 100, nthin = 1, nch = 3))

p <- Gro_pred(data = dat, 
              out = out$model, 
              title =out$wAIC_tab$model[1])
p$summary
p$predictions
p$GOF
p$plot_pred
p$convergence
p$posterior
```


```{r tests-Gro_pred}
Age <- sample(c(0:10), 1000, replace = TRUE)
MeasurementValue <- exp(0.2+15 * (1 - exp(-(0.1) * log(Age+1)))+ rnorm(1000,0,0.01))-1 
AnimalAnonID <- sample(c(0:20), 100, replace = TRUE)
dat = data.frame(Age = Age, MeasurementValue = MeasurementValue, 
                 AnimalAnonID = AnimalAnonID, MeasurementType = "Live Weight")
out = dat %>% Gro_analysis()


test_that(
  "Gro_pred",
  { 
    p<- dat %>% Gro_pred(out$model)
    expect_named(p,c("summary", "predictions", "plot_pred", "posterior", "convergence", "GOF"))
    expect_length(p$plot_pred$layers,3)
   expect_named(p$summary,c("mean", "sd", "QI 2.5", "QI 97.5", "Rhat"))
   expect_named(p$predictions,c("Age", "mean" , "Conf_Int_low", "Conf_Int_up" ))
   expect_named(p$GOF,c("normal", "X", "var" ,"conv"))
   expect_true("ggplot" %in% class(p$posterior))
expect_true("ggplot" %in% class(p$convergence))
})
```





```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_main.Rmd", vignette_name = "run growth models")
```
